Nested sampling with two objective functions

### 2016-02-06 Paper/ms.tex
equations
murray

@@

>>>>

The posterior for the underlying image given the data is
\begin{eqnarray}
p(\boldsymbol{m} | \boldsymbol{D})
&=& \frac{p(\boldsymbol{m})p(\boldsymbol{D}|\boldsymbol{m})}
{\int p(\boldsymbol{m})p(\boldsymbol{D}|\boldsymbol{m}) \,d^n\boldsymbol{m}}\\
&=& \frac{\exp\left[-\lambda \sum_i m_i\ln m_i
-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}m_{j}\right)^2\right]}
{\int \exp\left[-\lambda \sum_i m_i\ln m_i
-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}m_{j}\right)^2\right]\, d^n\boldsymbol{m}}
\end{eqnarray}

Therefore, this is a `doubly intractable' problem, closely related to
those studied (and solved) by \citep{murray}.

@@

\bibitem[Murray(2012)]{murray} Murray, Iain, Ghahramani, Zoubin, and MacKay, David.
``MCMC for doubly-intractable distributions.'' arXiv preprint arXiv:1206.6848 (2012).
